---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rrplot

<!-- badges: start -->
[![R-CMD-check](https://github.com/Riksrevisjonen/rrplot/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Riksrevisjonen/rrplot/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The purpose of rrplot is to provide auditors at OAG Norway with the ability to quickly make beautiful graphs with ggplot2 that are in accordance with official requirements.

## Installation

You can install the development version of rrplot from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Riksrevisjonen/rrplot")
```

## Contents

The package contains custom wrappers for the following geom functions in `ggplot2`:

* `geom_bar()` -> `geom_bar_RR()` 
* `geom_point()` -> `geom_point_RR()` 
* `geom_jitter()` -> `geom_jitter_RR()` 
* `geom_density()` -> `geom_density_RR()` 
* `geom_line()` -> `geom_line_RR()` 

Using the custom wrappers are optional, but recommended. 

## Example

This is a basic example which shows you how to create a bar chart:

```{r warning=FALSE, message=FALSE}
library(ggplot2)
library(ggthemes)
library(rrplot)

mtcars |> 
  ggplot(aes(x = factor(cyl),
             fill = factor(am))) +
  theme_RR() +
  geom_bar_RR() +
  labs(title = "Number of Cars per Number of Cylinders", 
       x = "Number of Cylinders", 
       y = "Count") +
  scale_fill_RR()

```

`theme_RR()` contains the custom theme and aesthetic adjustments, while `geom_bar_RR()` contains adjustments to the default settings in the bar plot geom. `geom_bar_RR()` accepts the same arguments as `geom_bar()`.

Note that `theme_RR()` needs to be placed **before** `geom_bar_RR()` as a layer in the ggplot call.

Another example, with a scatter plot:

```{r warning=FALSE}

iris |> 
  ggplot(aes(x = Sepal.Length, 
             y = Sepal.Width, 
             color = Species)) +
  theme_RR() +
  geom_point_RR() +
  labs(title = "Scatterplot of Sepal Dimensions", 
       x = "Sepal Length", 
       y = "Sepal Width") +
  scale_color_RR()

```


