---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(ggplot2)
library(rrplot2)
```

# rrplot2

<!-- badges: start -->

[![R-CMD-check](https://github.com/Riksrevisjonen/rrplot2/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Riksrevisjonen/rrplot2/actions/workflows/R-CMD-check.yaml)

<!-- badges: end -->

The purpose of rrplot2 is to provide auditors at OAG Norway with the ability to quickly make beautiful graphs with ggplot2 that are in accordance with official requirements.

## Installation

You can install the development version of rrplot2 from the local repository with:

``` r
install.packages("rrplot2", repos = "https://cran.riksrevisjonen.no/latest") 
```

## Contents

### Main theme

Most of the adjustments to the graph aesthetics can be found in the `theme_RR()` function. This is simply added as a layer in the ggplot call.

### Custom wrappers for specific geoms

The package also contains custom wrappers for the following geom functions in `ggplot2`:

-   `geom_bar()` -\> `geom_bar_RR()`
-   `geom_point()` -\> `geom_point_RR()`
-   `geom_jitter()` -\> `geom_jitter_RR()`
-   `geom_density()` -\> `geom_density_RR()`
-   `geom_line()` -\> `geom_line_RR()`

These wrappers are also added as layers in the ggplot call, along with `theme_RR()`. Note that `theme_RR()` needs to be placed **before** the geom wrapper (see example below). Using the custom wrappers are optional, but recommended.

### Color scales

The package contains functions to determine the color palette of your graphs.

Discrete color palette functions:

-   `scale_color_RR()`: Used when the **color** argument of `aes()` has been assigned.
-   `scale_fill_RR()`: Used when the **fill** argument of `aes()` has been assigned.

These are added as separate layers in the ggplot call and contain 9 colors:

```{r warning=FALSE, fig.height=3}
library(scales)
show_col(RR_pal()(9))
```

Continuous color palette functions:

-   `scale_fill_continuous_RR_red`: Red continuous **fill** scale between `#fcb7b9` and `#a40000`
-   `scale_fill_continuous_RR_blue` Blue continuous **fill** scale between `#b4c6e9` and `#001b61`
-   `scale_color_continuous_RR_red` Red continuous **color** scale between `#fcb7b9` and `#a40000`
-   `scale_color_continuous_RR_blue` Blue continuous **color** scale between `#b4c6e9` and `#001b61`

## Examples

This is a basic example which shows you how to create a bar chart:

```{r warning=FALSE}
library(ggplot2)
library(rrplot2)

mtcars |>
  ggplot(aes(x = factor(cyl),
             fill = factor(am))) +
  theme_RR() +
  geom_bar_RR() +
  labs(title = "Dette er et søylediagram",
       subtitle = "Fordelt på undergrupper",
       x = "Gruppe",
       y = "Antall",
       fill = "Kategori") +
  scale_fill_RR()
```

Note that `geom_bar_RR()` accepts the same arguments as `geom_bar()`. Again, please note that `theme_RR()` needs to be placed **before** the `geom_bar()` layer.

Another example, with a scatter plot:

```{r warning=FALSE}

iris |>
  ggplot(aes(x = Sepal.Length,
             y = Sepal.Width,
             color = Species)) +
  theme_RR() +
  geom_point_RR() +
  labs(title = "Scatterplot",
       subtitle = "Dette er en lenger beskrivelse over flere linjer\nsom gir leseren mer informasjon.",
       x = "X-variabel",
       y = "Y-variabel") +
  scale_color_RR()

```
